Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-06-24 ms.tex
changes from yesterday

\shorttitle{Lyman $\alpha$}
\shortauthors{McClellan et al.}

@@

\section{To Do List}
$\square$ Change all plots to use just wing line profile, exclude Doppler core

$\square$ Use larger n phot MC runs for tau=1e5

>>>>

\shorttitle{Resonant Scattering of \lya}
\shortauthors{McClellan et al.}

@@

\section{To Do List}
$\blacksquare$ Change all plots to use just wing line profile, exclude Doppler core

$\blacksquare$ Use larger n phot MC runs for tau=1e5
